\documentclass[sigconf]{acmart}

\newcommand{\FIXME}[1]{{\color{red}{\textbf{FIXME:} #1}}}
\newcommand{\amdrev}[1]{{\color{blue}{#1}}}
\newcommand{\amd}[1]{{\color{blue}{[\textbf{AMD Comment:} #1]}}}
\newcommand{\lei}[1]{{\color{cyan}{[\textbf{Lei Comment:} #1]}}}
\newcommand{\hg}[1]{{\color{green}{[\textbf{Hans Comment:} #1]}}}



\usepackage{booktabs} % For formal tables

% Copyright
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}


% DOI
\acmDOI{10.475/123_4}

% ISBN
\acmISBN{123-4567-24-567/08/06}

%Conference
\acmConference[NetCompute'18]{ACM SIGCOMM 2018 Workshop on In-Network Computing conference}{August 2018}{Budapest, Hungary} 
\acmYear{2017}
\copyrightyear{2017}

\acmPrice{15.00}

\usepackage{xspace}
\newcommand{\OurSys}{Wharf\xspace}

\usepackage{algorithm2e}
\usepackage{listings}

\begin{document}
\title{In-network computing to the rescue of faulty links}
%\title{SIG Proceedings Paper in LaTeX Format}
%\titlenote{Produces the permission block, and copyright information}
%\subtitle{Extended Abstract}

\author{Hans Giesen}
\affiliation{\institution{University of Pennsylvania}}
\author{Lei Shi}
\affiliation{\institution{University of Pennsylvania}}
\author{John Sonchack}
\affiliation{\institution{University of Pennsylvania}}
\author{Anirudh Chelluri}
\affiliation{\institution{University of Pennsylvania}}
\author{Nishanth Prabhu}
\affiliation{\institution{University of Pennsylvania}}
\author{Nik Sultana}
\affiliation{\institution{University of Pennsylvania}}
\author{Latha Kant}
\affiliation{\institution{Vencore Labs}}
\author{Anthony J McAuley}
\affiliation{\institution{Vencore Labs}}
\author{Alexander Poylisher}
\affiliation{\institution{Vencore Labs}}
\author{Andr\'e DeHon}
\affiliation{\institution{University of Pennsylvania}}
\author{Boon Thau Loo}
\affiliation{\institution{University of Pennsylvania}}

%\author{Firstname Lastname}
%\authornote{Note}
%\orcid{1234-5678-9012}
%\affiliation{%
%  \institution{Affiliation}
%  \streetaddress{Address}
%  \city{City} 
%  \state{State} 
%  \postcode{Zipcode}
%}
%\email{email@domain.com}
%
%\author{Firstname Lastname}
%\orcid{1234-5678-9012}
%\affiliation{%
%  \institution{Affiliation}
%  \streetaddress{Address}
%  \city{City} 
%  \state{State} 
%  \postcode{Zipcode}
%}
%\email{email@domain.com}
%
%\author{Firstname Lastname}
%\orcid{1234-5678-9012}
%\affiliation{%
%  \institution{Affiliation}
%}
%\email{email@domain.com}
%
%\author{Firstname Lastname}
%\orcid{1234-5678-9012}
%\affiliation{%
%  \institution{Affiliation}
%}
%\email{email@domain.com}
%
%\author{Firstname Lastname}
%\orcid{1234-5678-9012}
%\affiliation{%
%  \institution{Affiliation}
%}
%\email{email@domain.com}


% The default list of authors is too long for headers}
%\renewcommand{\shortauthors}{F. Lastname et al.}
\renewcommand{\shortauthors}{H. Giesen et al.}

\begin{abstract}
Failing network links are usually disabled, and packets are routed around them
until the links are repaired. While
it is often possible
to utilize some of a failing link's capacity, losing
what remains of a link's
capacity is typically deemed preferable to the erratic effect that unreliable links can
have on application-level behavior.

We describe a new network function that relies on in-network computing to limit
the erratic effect of failing network links, to enable the continued use of
those links until they can be repaired.
%We argue that such a network function can help mitigate rolling
%failures in datacenter networks, and that our design can interoperate
%with existing network architecture and configuration choices, such as
%for multi-path routing.

We explore the design space using ns-3, and evaluate our
implementation on a physical test-bed that includes programmable
switches and reconfigurable hardware.
Our current hardware prototype uses around 10\% of our FPGA's
resources while operating at \FIXME{30\%} of its maximum clock rate,
but can almost saturate a 10GbE link.
\hg{The current frequency of 156.25 MHz is determined by the line rate
    (=10000/64).  Higher frequencies won't benefit the throughput as the
    link will be the bottleneck.  This gives the false impression that
    a higher frequency would be better.  I would rather mention latency
    or even power consumption.}
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>  
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Embedded systems}
\ccsdesc[300]{Computer systems organization~Redundancy}
\ccsdesc{Computer systems organization~Robotics}
\ccsdesc[100]{Networks~Network reliability}

% We no longer use \terms command
%\terms{Theory}

\keywords{ACM proceedings}


\maketitle

\input{introduction}
\input{background}
\input{design}
\input{implementation}
\input{evaluation}
\input{conclusion}

\subsection*{Acknowledgements}
This material is based upon work supported by the Defense Advanced
Research Projects Agency (DARPA) under Contract No. HR001117C0047.
Xilinx provided tools and IP, including SDNet to support P4 to FPGA
compilation, the Ethernet MAC, and HLS and physical design mapping
software. 

\bibliographystyle{ACM-Reference-Format}
\bibliography{paper}

\end{document}
